SMT-Boosted Security Types for Low-Level MPC

### 2025-11-24 toplas26/sty.tex
checkpoint

Our approach to static confidentiality analysis is to enforce the use of sound
techniques in semi-homomorphic encryption in protocols.  As discussed in
the example in Section \ref{section-smt-example}, protocols integrate
interactive elements, such as the sharing of one-time-pad (OTP)
encrypted secrets, and noninteractive elements, such as addition (of
shares). To comport with this we introduce distinct judgement forms for
interactive and noninteractive protocol elements. Our type system
as presented will assume 2-client protocols, but this is for
clarity of presentation and the analysis can be generalized to more parties.

@@

guarantees confidentiality (Theorem \ref{theorem-OK})$.

@@

In addition to typing judgements, in order to show that a protocol is
secure, we need to classify all corrupt views as shares, all
public values as secure openings, and all outputs as reconstructed
shares. We capture this formally with the following notion of
type environment closure.
\begin{definition}
  \label{def-sty-closed}
  $\Gamma$ is \emph{closed for $\prog$} iff for all $H,C$,
  for all $x \in \houtputs$ there exists $\phi$ such that either
  $([x,\phi] : \sharety) \in \Gamma$ if $C = \setit{1}$
  or  $([\phi,x] : \sharety) \in \Gamma$ if $C = \setit{2}$,
  and for all $\out{\cid} \in O$ we have $(\pubx{\out{\cid}} : \outty) \in \Gamma$.
\end{definition}
Now, the following is a consequence of Definitions \ref{def-OK} and \ref{def-sty-closed}, and then
our main Theorem \ref{theorem-sty} follows by Lemma \ref{lemma-OK} and Theorem \ref{theorem-OK}.
\begin{theorem}
  \label{theorem-OK}
  If $\prog,\Gamma,R : {OK}$ and $\Gamma$ is closed
  for $\prog$, then $\prog$ satisfies noninterference modulo output. 
\end{theorem}
\begin{proof}
  Let $\iov(\prog) = S \cup V \cup O$ and assume some partitioning $H,C$.
  %For any $\out{\cid} \in O$ with $\Gamma,\toeq{\prog} \vdash \pubx{\out{\cid}} : \outty$
  %we can assume wlog that $(\out{\cid} : \outty) \in \Gamma$, since we can
  %add the binding to $\Gamma'$ with  $\prog,\Gamma',R  : {OK}$ by Lemma
  %\ref{lemma-OK}.
  By Definitions \ref{def-sty-closed} we know that every $x \in \houtputs$
  occurs in some $\stt$ with $(\stt, \sharety) \in \Gamma$, and
  that $(\out{\cid} : \outty) \in \Gamma$ for all $\out{\cid} \in O$.
  Therefore by Definition \ref{def-OK} (and marginalizing away
  extraneous $(\stt : \sty) \in \Gamma$) we have:
  $$
  \condd{\progd(\prog)}{S_H}{S_C \cup O} = \condd{\progd(\prog)}{S_H}{S_C \cup V_C \cup O}
  $$
  which is noninterference modulo output by Definition \ref{definition-NIMO}.
\end{proof}

>>>>

Our approach to static confidentiality analysis is to enforce the use of sound
techniques in semi-homomorphic encryption in protocols.  As discussed in
the example in Section \ref{section-smt-example}, protocols integrate
interactive elements, such as the sharing of one-time-pad (OTP)
encrypted secrets, and noninteractive elements, such as addition (of
shares). To comport with this we introduce distinct judgement forms for
interactive and noninteractive protocol elements. Our type system
as presented will assume 2-client protocols, but this is for
clarity of presentation and the analysis can be generalized to more parties.
We define the federation as $\setit{1,2}$ (client 1 and client 2).

@@

guarantees confidentiality (Theorem \ref{theorem-OK}).

@@

In addition to typing judgements, in order to show that a protocol is
secure, we need to classify all corrupt views as shares, all
public values as secure openings, and all outputs as reconstructed
shares by adding them to $\Gamma$. We capture this formally with the following notion of
type environment closure.
\begin{definition}
  \label{def-sty-closed}
  $\Gamma$ is \emph{closed for $\prog$} iff for all $H,C$,
  for all $x \in \houtputs$ there exists $\phi$ such that either
  $([x,\phi] : \sharety) \in \Gamma$ if $C = \setit{1}$
  or  $([\phi,x] : \sharety) \in \Gamma$ if $C = \setit{2}$,
  and for all $\out{\cid} \in O$ we have $(\pubx{\out{\cid}} : \outty) \in \Gamma$.
\end{definition}
Now, the following is a consequence of Definitions \ref{def-OK} and \ref{def-sty-closed}, and then
our main Theorem \ref{theorem-sty} follows by Lemma \ref{lemma-OK} and Theorem \ref{theorem-OK}.
\begin{theorem}
  \label{theorem-OK}
  If $\prog,\Gamma,R : {OK}$ and $\Gamma$ is closed
  for $\prog$, then $\prog$ satisfies noninterference modulo output. 
\end{theorem}
\begin{proof}
  Let $\iov(\prog) = S \cup V \cup O$ and assume some partitioning $H,C$
  with $H = \setit{b}$ and $C = \setit{a}$ for $a,b \in \setit{1,2}$.
  %For any $\out{\cid} \in O$ with $\Gamma,\toeq{\prog} \vdash \pubx{\out{\cid}} : \outty$
  %we can assume wlog that $(\out{\cid} : \outty) \in \Gamma$, since we can
  %add the binding to $\Gamma'$ with  $\prog,\Gamma',R  : {OK}$ by Lemma
  %\ref{lemma-OK}.
  Let $\Phi_a$ and $\Phi^o$ be as defined in Definition \ref{def-OK}. 
  By Definitions \ref{def-sty-closed} we have that $x \in \houtputs$
  implies $x \in \Phi_a$ and $(\out{\cid} : \outty) \in \Gamma$ for all
  $\out{\cid} \in O$. 
  Therefore by Definition \ref{def-OK} (and marginalizing away
  extraneous $(\stt : \sty) \in \Gamma$) we have:
  $$
  \condd{\progd(\prog)}{S_H}{S_C \cup O} = \condd{\progd(\prog)}{S_H}{S_C \cup V_C \cup \Phi^p \cup O}
  $$
  By definition of $\TirName{Output}$ it is also the case that for all
  $\out{\cid} \in O$ we have $\toeq{\prog} \models o = \phi$ for some
  $\phi \in \Phi^o$. Therefore we have:
  $$
  \condd{\progd(\prog)}{S_H}{S_C \cup O} = \condd{\progd(\prog)}{S_H}{S_C \cup V_C \cup O}
  $$
  which is noninterference modulo output by Definition \ref{definition-NIMO}.
\end{proof}
